---
title: "A03_G28512359"
author: "JINGSI WU"
date: "9/16/2018"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

To start solving the questions, we need to load the dataset and do some data prepocessing.

First we read our dataset.
```{r kickfootball}
mydf <- read.csv("kicksfootball.csv")
summary(mydf)
```

As we can see in the summary, there are upper and lower "y" in the dataset, both "y" represent Melvin has reached his goal.
So when we change catagorical data to dummy variables, "y" also need to be difined.
```{r data prepocessing}
mydf$prac_mat_bin <- ifelse(mydf$practiceormatch == "P", 1, 0)
mydf$gbin <- ifelse(mydf$goal == "Y"|mydf$goal == "y", 1, 0) 

```

Data preprocessing has done! Now let's start solving the problems.

## Part A

First we need to check some key information of the dataset.
```{r kickfoodball}
str(mydf)

```

As you can see, there are 952 observations in the dataset. Now let's count how many times did Melvin succeed. 
```{r Melvin succeed}
summary(mydf)
```

The probability that Melvin is going to reach his goal is
```{r goal}
goalreach <- (742+17)/952
print(goalreach)
```


## Part B

To build the practice and match model, we need to seperate the data first.
```{r seperate data}
gbin_prac <- subset(mydf, mydf$prac_mat_bin == 1)
gbin_mat <- subset(mydf, mydf$prac_mat_bin == 0)
```

Then we can fit the data into the logistic regression model and see the result.
```{r logistic}
goal_prac.mod <- glm(gbin ~ yards, 
               data = gbin_prac,
               family = binomial)

goal_mat.mod <- glm(gbin ~ yards, 
                     data = gbin_mat,
                     family = binomial)
summary(goal_prac.mod)
summary(goal_mat.mod)
```

The regression model seems no problem, so now we can strat to predict Melvin's performance.
```{r}
pred <- c(20, 40, 60)
newdata  = data.frame(yards = pred)
predict(goal_prac.mod, newdata, type = "response")
predict(goal_mat.mod, newdata, type = "response")
```

The probability of Melvin scoring a goal when he kicks from 20, 40 and 60 yards in practice is 0.94, 0.76, 0.39.
Theprobability of Melvin scoring a goal when he kicks from 20, 40 and 60 yards in match is 0.97, 0.76, 0.22.
The probability is different.

## Part C

Before we start to plot, we need to reorganize the data and create a new dataset. I'm going to predict the performance of Melvin from 15 yards to 75 yards. Also, for each value we must create a corresponding lable.
```{r ggplot prepare}
yard_plot <- data.frame(seq(15,75,1)) 
colnames(yard_plot) <- "yards"
prac_label <- data.frame(rep("Practice", 61))
prac_plot <- data.frame(yard_plot, predict(goal_prac.mod, yard_plot, type = "response"), prac_label)
mat_label <- data.frame(rep("Match", 61))
mat_plot <- data.frame(yard_plot, predict(goal_mat.mod, yard_plot, type = "response"), mat_label)

```

Then we give the dataset above same column names so that we can combine them together
```{r combine }
colnames(mat_plot) <- c("yards", "probability", "labels")
colnames(prac_plot) <- c("yards", "probability", "labels")
plotset <- rbind(prac_plot, mat_plot)
```

Finally, use ggplot2 to get the picture
```{r plot data}
ggplot(plotset,aes(x = yards, y = probability, col = labels ))+ 
  geom_line()+
  xlim(c(10,75))+
  ylim(c(0,1))+
  labs(x='Yards',y='Probability of Melvin scoring', title = "Probability of Malvin score in match&practice" )
```

